%% The MIT License (MIT)
%%
%% Copyright (c) 2015 Daniil Belyakov
%%
%% Permission is hereby granted, free of charge, to any person obtaining a copy
%% of this software and associated documentation files (the "Software"), to deal
%% in the Software without restriction, including without limitation the rights
%% to use, copy, modify, merge, publish, distribute, sublicense, and/or sell
%% copies of the Software, and to permit persons to whom the Software is
%% furnished to do so, subject to the following conditions:
%%
%% The above copyright notice and this permission notice shall be included in all
%% copies or substantial portions of the Software.
%%
%% THE SOFTWARE IS PROVIDED "AS IS", WITHOUT WARRANTY OF ANY KIND, EXPRESS OR
%% IMPLIED, INCLUDING BUT NOT LIMITED TO THE WARRANTIES OF MERCHANTABILITY,
%% FITNESS FOR A PARTICULAR PURPOSE AND NONINFRINGEMENT. IN NO EVENT SHALL THE
%% AUTHORS OR COPYRIGHT HOLDERS BE LIABLE FOR ANY CLAIM, DAMAGES OR OTHER
%% LIABILITY, WHETHER IN AN ACTION OF CONTRACT, TORT OR OTHERWISE, ARISING FROM,
%% OUT OF OR IN CONNECTION WITH THE SOFTWARE OR THE USE OR OTHER DEALINGS IN THE
%% SOFTWARE.

% The font could be set to Windows-specific Calibri by using the 'calibri' option
\documentclass[]{mcdowellcv}

% For mathematical symbols
\usepackage{amsmath}

% Set applicant's personal data for header
\name{\underline{Wong} Zhao Wu, Bryan}
\address{}
\webpage{kiritowu.github.io}
\call{(+65) XXXX XXXX}
\email{zhaowu.wong@gmail.com}
\github{github.com/kiritowu}
\linkedin{linkedin.com/in/zw-wong}

\begin{document}

	% Print the header
	\makeheader
	
	% Print the content

	\begin{cvsection}{Employment}
		
		
		
		
		\begin{cvsubsection}{Co-Founder, AI Engineer}{Flora Softworks Pte Ltd}{Feb 2022 - Apr 2023}
			\begin{itemize}
			
				\item Co-Founded and developed Flora, a SaaS enterprise search solution using docarray and elasticsearch.
			
				\item Presented Flora to 10+ potential clients, resulting in 1 successful pilots.
			
			\end{itemize}
		\end{cvsubsection}
		
		
		
		\begin{cvsubsection}{AI Engineer Intern}{ANOR Technologies Pte Ltd}{Sep 2022 - Feb 2023}
			\begin{itemize}
			
				\item Modularize and optimized signal processing logic into Python functions from multiple research-oriented software (e.g. Matlab, Origin).
			
				\item Supported research project by analyzing data and presenting experiment insights to relevant stakeholders.
			
				\item Developed FastAPI backend for the no-code data analysis and signal processing application for Terahertz spectrogram samples.
			
			\end{itemize}
		\end{cvsubsection}
		
		
		
		
	\end{cvsection}
	
	\begin{cvsection}{Education}
		
		\begin{cvsubsection}{National University of Singapore}{}{Aug 2025 -- Jul 2029}
			\begin{itemize}
				
				\item B.Comp. in Computer Science with NUS College.
				
				\item Recipient of NUS ASEAN Undergraduate Scholarship.
				
			\end{itemize}
		\end{cvsubsection}
		
		\begin{cvsubsection}{Singapore Polytechnic}{}{Apr 2020 -- Apr 2023}
			\begin{itemize}
				
				\item Diploma with Merit in Applied AI and Analytics, GPA 4.0/4.0.
				
				\item Recipient of IMDA Gold Medal and SP Scholarship.
				
				\item Graduate Coursework: Machine Learning, Deep Learning, DevOps, Data Analytics, Data Engineering, Data Visualisation.
				
			\end{itemize}
		\end{cvsubsection}
		 
	\end{cvsection}
		
    \begin{cvsection}{Technical Experience}
        \begin{cvsubsection}{Projects}{}{}
            \begin{itemize}
				
				
				
				\item \textbf{OwlShield} (2024). LLM Safety Firewall that validates user inputs and LLM outputs against adversarial attacks for organization’s LLM applications.
				
				
				
				\item \textbf{Neural Information Retrieval System} (2022). Neural Search to retrieval engine for unstructured text documents.
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
				
            \end{itemize}
        \end{cvsubsection}
	\end{cvsection}

	\begin{cvsection}{Additional Experience and Certification}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item \textbf{Google Cloud Certified Professional Machine Learning Engineer:} Certified in designing, building, and productionizing ML solutions on Google Cloud. (ID: 43ffb52bffed42bbad16545107dd7723)
				
				\item \textbf{Chairperson, AI Student Developer Conference 2023:} (2023): Led a diverse student team, partnered with industry leaders, moderated fireside chats, and developed gamified companion app, driving success of inaugural conference with 300+ AI youth participants.
				
				\item \textbf{Founder \& President, SP Artificial Intelligence (SPAI) Student Chapter:} (2021): Moulded a community of AI Enthusiast in SP through workshops, competition and student-led projects, resulted in an Outstanding Contributions (Group) Excellence Award and 200 members within the first year of existence.
				
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
	\begin{cvsection}{Technologies and Skills}
		\begin{cvsubsection}{}{}{}	
			\begin{itemize}
				\item Python, SQL, Typescript, Javascript, HTML, CSS, Bash, \LaTeX
				\item Pytorch, Huggingface, Scikit-Learn, FastAPI, Numpy, Pandas, Matplotlib, Seaborn, MySQL, PostgressSQL, MongoDB, Node.js, Fastify, Git
				\item Docker, Kubernetes, Google Cloud (GCP), Firebase, Supabase
				\item Natural Leader, Team Player, Fast Learner, Critical Thinker
			\end{itemize}
		\end{cvsubsection}
	\end{cvsection}
	
\end{document}